The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-26 paper/ms.tex
addition to paper spectra section

To derive stellar parameters from our TRES spectra, we initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values. The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}. Individual elemental abundances are extracted both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}. The results of these absolute abundance calculations are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.

@@

\subsection{Red Giants}
\label{rgs}

\subsection{Other Stars}
\label{other}

>>>>

To derive stellar parameters from our TRES spectra, we initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values. The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and chemical abundances for 20 chemical species are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}. BACCHUS uses an interpolation scheme through a grid of MARCS model atmospheres \citep{Gustafsson2008} in combination with TURBOSPECTRUM \citep{Alvarez1998, Plez2012}. For the calculation of synthetic spectra, atomic line information has been taken from the fifth version of the Gaia-ESO linelist (Heiter et al., in preparation). Additionally we used the molecular species for CH \citep{Masseron2014}, CN, NH, OH, MgH  C$_{2}$ (T. Masseron, private communication). The SiH molecular information is adopted from the Kurucz linelists and the information for TiO, ZrO, FeH, CaH from B. Plez (private communication).

Individual elemental abundances are derived by first fixing the stellar atmospheric parameters to those determined above. Spectra are then synthesized  in regions centered around an absorption  feature of the element we want to derive. The spectra generated will have different [X/Fe] values. A $\chi^2$ minimization procedure is then done to derive the best fitting abundance for each line. The reported abundances are the median [X/Fe] value of the various line regions for a given element. To achieve the most precise abundances we have derived them using  both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}. The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}. Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material. No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.

@@

\subsection{Red Giants}
\label{rgs}
\subsection{Chemical Composition}
place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys 
\subsection{Other Stars}
\label{other}
